Gammapy: A Python package for gamma-ray astronomy

### 2023-01-30 src/ms-review.tex
Fix IRF figure caption

\subsection{gammapy.irf}
\label{ssec:gammapy-irf}
%
%
\begin{figure*}[ht!]
	\centering
	\includegraphics[width=1.\textwidth]{figures/irfs.pdf}
	\caption{
		Using \code{gammapy.irf} to read and plot instrument response functions.
		The left panel shows the effective area as a function of energy for
		the \cta, \hess, \magic, \hawc and \fermi instruments. The right panel shows
		the $68\%$ containment radius o as a function of energy for the \cta, \hess
		and \fermi instruments. These IRFs do not correspond to the latest
		performance of the instruments, but still are representative of the 
		detector type and energy range. We also neede to rely on publicly available
		data. The \cta IRFs are from the \textit{prod5} production. The \hess IRFs are from the DL3 DR1,
        using observation ID 033787. The \magic effective area is computed for a
        $20\,{\rm min}$ observation at the Crab Nebula coordinates. The
		\fermi IRFs use \textit{pass8} data and are also taken at the position of the Crab Nebula.
		The \hawc effective area is shown for the event classes $N_{Hit}=5 - 9$ as light gray
		lines along with the sum of all event classes as a black line. The \hawc IRFs are taken from
		the first public release of event data the \hawc collaboration. All 
		data is also availabe in the \code{gammapy-data} repository.
    }
	\label{fig:irfs}
\end{figure*}
%

>>>>

\subsection{gammapy.irf}
\label{ssec:gammapy-irf}
%
%
\begin{figure*}[ht!]
	\centering
	\includegraphics[width=1.\textwidth]{figures/irfs.pdf}
	\caption{
		Using \code{gammapy.irf} to read and plot instrument response functions.
		The left panel shows the effective area as a function of energy for
		the \cta, \hess, \magic, \hawc and \fermi instruments. The right panel shows
		the $68\%$ containment radius of the PSF as a function of energy for the \cta, \hess
		and \fermi instruments. The \cta IRFs are from the \textit{prod5} production. The \hess IRFs are from the DL3 DR1,
        using observation ID 033787. The \magic effective area is computed for a
        $20\,{\rm min}$ observation at the Crab Nebula coordinates. The
		\fermi IRFs use \textit{pass8} data and are also taken at the position of the Crab Nebula.
		The \hawc effective area is shown for the event classes $N_{Hit}=5 - 9$ as light gray
		lines along with the sum of all event classes as a black line. The \hawc IRFs are taken from
		the first public release of event data the \hawc collaboration. All IRFs do not correspond
		to the latest performance of the instruments, but still are representative of the 
		detector type and energy range. We also exclusively relied on publicly available
		data provided by the collaborations. The data is also availabe in the
		\code{gammapy-data} repository.
    }
	\label{fig:irfs}
\end{figure*}
%
